---
title: "QMM Assignment4"
author: "Manaswini"
date: "2022-10-19"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

Objective Function 

$$MinimizeTC = 622x_{11}+614x_{12}+630x_{13}+641x_{21}+645x_{22}+649x_{23}$$
These are subject to the following constraints
$$
x_{11}+x_{12}+x_{13}>=100$$
$$
x_{21}+x_{22}+x_{23}>=120$$

these are the supply constraints

$$
x_{11}+x_{21}>=80$$
$$
x_{12}+x_{22}>=60$$
$$
x_{13}+x_{23}>=70$$


```{r}
library(Matrix) 
library("lpSolve") 
display <- matrix(c(22,14,30,600,100, 
16,20,24,625,120, 
80,60,70,"-","210/220"),ncol=5,nrow=3,byrow=TRUE) 
colnames(display) <- c("Warehouse1","Warehouse2","Warehouse3","Prod Cost","Prod Capacity") 
rownames(display) <- c("PlantA","PlantB","Monthly Demand") 
display <- as.table(display) 
display 

```
## Warehouse1 Warehouse2 Warehouse3 Prod Cost Prod Capacity 
## PlantA 22 14 30 600 100  
## PlantB 16 20 24 625 120  
## Monthly Demand 80 60 70 - 210/220 


Being the capacity is equal to 220 and Demand is equal to 210 we need to add a “dummy” row where a Warehouse4 would be. It will contain 0 and 0 for each of the plants and the dummy will add to the total up to 220. The table would then look like this: 
```{r}
display1 <- matrix(c(622,614,630,0,100, 
641,645,649,0,120, 
80,60,70,10,220),ncol=5,nrow=3,byrow=TRUE) 
colnames(display1) <- c("Warehouse1","Warehouse2","Warehouse3","Dummy","Production Capacity") 
rownames(display1) <- c("PlantA","PlantB","Monthly Demand") 
display1 <- as.table(display1) 
display1 





```


This table now satisfies the need for a balanced problem. Now we are ready to solve within R. First we want to
```{r}

costs <- matrix(c(622,
614,630,0, 
641,645,649,0),nrow=2, byrow = TRUE)

```

Next we will identify the Production Capacity in the row of the matrix: 
```{r}
row.rhs <- c(100,120) 
row.signs <- rep("<=", 2) 


```
Then we will identify the Monthly Demand with double variable of 10 at the end. Above we added the 0,0 in at the end of each of the columns:
```{r}
col.rhs <- c(80,60,70,10) 
col.signs <- rep(">=", 4) 


```

Now we are ready to run LP Transport command: 
```{r}
lp.transport(costs,"min",row.signs,row.rhs,col.signs,col.rhs)
```
Here is the solution matrix:
```{r}
lp.transport(costs, "min", row.signs, row.rhs, col.signs, col.rhs)$solution 

```
This gives us the following that dollars. This gives us the following results for each of the variables:$$60x_{12}$$which is Warehouse 2 from Plant A.

$$40x_{13}$$which is Warehouse 3 from Plant A.
$$80x_{21}$$which is Warehouse 1 from Plant B.
$$30x_{23}$$which is Warehouse 3 from Plant B.and because “10” shows up in the 4th variable$$10x_{24}$$it is a “throw-away variable”
This would complete the answer for question 1.
We know that number of variables in primal is equal to the number of constants in dual. The first question is the primal of the
LP. Since we took the minimization in the primal we will maximize in the dual. Let’s use the variables u and v for the dual problem

```{r}
display2 <- matrix(c(622,614,630,100,"u_1", 
641,645,649,120,"u_2", 
80,60,70,220,"-", 
"v_1","v_2","v_3","-","-"),ncol=5,nrow=4,byrow=TRUE) 
colnames(display2) <- c("W1","W2","W3","Prod Cap","Supply (Dual)") 
rownames(display2) <- c("PlantA","PlantB","Monthly Demand","Demand (Dual)") 
display2 <- as.table(display2) 
display2 


```
From here we are going to create our objective function based on the constraints from the primal. Then use the objective
function from the primal to find the constants of the dual.
Maximize Z = $$100u_{1}+120u_{2}+80v_{1}+60v_{2}+70v_{3}$$
this objective function is subject to the following constraints
$$u_{1}+_v{1}<=622$$
$$u_{1}+v_{2}<=614$$
$$u_{1}+v_{3}<=630$$
$$u_{2}+v_{1}<=641$$
$$u_{2}+v_{2}<=645$$
$$u_{2}+v_{3}<=649$$
These constants are taken from the transposed matrix of the Primal of Linear Programming function. An easy way to check
yourself is to transpose the f.con into the matrix and match to the constants above in the Primal. These are unrestricted
where where u=1,2 and v=1,2,3

```{r}
#Constants of the primal are now the objective function variables. 
f.obj <- c(100,120,80,60,70) 
#transposed from the constraints matrix in the primal 
f.con <- matrix(c(1,0,1,0,0, 
1,0,0,1,0, 
1,0,0,0,1, 
0,1,1,0,0, 
0,1,0,1,0, 
0,1,0,0,1),nrow=6, byrow = TRUE) 

#these change because we are MAX the dual not min 
f.dir <- c("<=", 
"<=", 
"<=", 
"<=", 
"<=", 
"<=") 
f.rhs <- c(622,614,630,641,645,649) 
lp ("max", f.obj, f.con, f.dir, f.rhs) 




```

```{r}
lp ("max", f.obj, f.con, f.dir, f.rhs)$solution

```
The minimal Z=132790 (Primal) and the maximum Z=139120(Dual). What are we trying to max/min in this problem. We
found that we should not be shipping from Plant(A/B) to all three Warehouses. We should be shipping from:
60 Units from Plant A to Warehouse 2.
40 Units from Plant A to Warehouse 3.
60 Units from Plant B to Warehouse 1.
60 Units from Plant B to Warehouse 3.
Now we want to Max the profits from each distribution in respect to capacity.
Now I have been working very hard to try and get the third question correct from the problem.
```{r}
row.rhs1 <- c(101,120) 
row.signs1 <- rep("<=", 2) 
col.rhs1 <- c(80,60,70,10) 
col.signs1 <- rep(">=", 4) 
row.rhs2 <- c(100,121) 
row.signs2 <- rep("<=", 2) 
col.rhs2 <- c(80,60,70,10) 
col.signs2 <- rep(">=", 4) 
lp.transport(costs,"min",row.signs,row.rhs,col.signs,col.rhs) 

```
```{r}
lp.transport(costs,"min",row.signs1,row.rhs1,col.signs1,col.rhs1) 

```

```{r}
lp.transport(costs,"min",row.signs2,row.rhs2,col.signs2,col.rhs2) 
```
```{r}
lp ("max", f.obj, f.con, f.dir, f.rhs)$solution 

```
CONCLUSION:
from the primal:
$$60x_{12}$$which is 60 Units from Plant A to Warehouse 2.
$$40x_{13}$$which is 40 Units from Plant A to Warehouse 3.
$$80x_{21}$$which is 60 Units from Plant B to Warehouse 1.
$$30x_{23}$$which is 60 Units from Plant B to Warehouse 3.
from the dual
We want the MR=MC. Five of the six MR<=MC. The only equation that does not satisfy this requirement is Plant B to
Warehouse 2. We can see that from the primal that we will not be shipping any AED device there.


