---
title: "Assignment4"
author: "Manaswini"
date: "10/27/2022"
output:
  word_document: default
  pdf_document: default
---

## Question 1 - Hope Valley Health Care Association

Problem Description -- The Hope Valley Health Care Association owns and operates six nursing homes in adjoining states. An evaluation of their efficiency has been undertaken using two inputs and two outputs. The inputs are staffing labor (measured in average hours per day) and the cost of supplies (in thousands of dollars per day). The outputs are the number of patient-days reimbursed by third-party sources and the number of patient-days reimbursed privately. A summary of performance data is shown in the table below.
```{r}
#loading package
require(Benchmarking)
```



```{r}
#  matrix for the two inputs
X <- matrix(c(150, 400, 320, 520, 350, 320, 0.2, 0.7, 1.2, 2.0, 1.2, 0.7), ncol = 2)
#  matrix for the two outputs
Y <- matrix(c(14000, 14000, 42000, 28000, 19000, 14000, 3500, 21000, 10500, 42000, 25000, 15000), ncol = 2)
colnames(X) <- c("Staff Hours per Day","Supplies per Day")
colnames(Y) <- c("Reimburse Patient-Days", "Privately Paid Patient-Days")
print(X)
print(Y)
```


```{r}
# DEA code utilizing the FDH method
FDH <- rep("FDH", times = 6)
Not_Applicable <- rep(NA, times = 6)
DEA_FDH <- dea(X, Y, RTS = "FDH")
DEA_FDH_Peers <- peers(DEA_FDH)                             
DEA_FDH_Lambda <- lambda(DEA_FDH)  
print(DEA_FDH)
print(DEA_FDH_Peers)
print(DEA_FDH_Lambda)
dea.plot.isoquant(X, Y, RTS= "FDH")
DEA_FDH_Peers <- cbind(DEA_FDH_Peers, Not_Applicable, Not_Applicable)
FDH_Summary <- cbind(FDH, DEA_FDH$eff, DEA_FDH_Peers, DEA_FDH_Lambda)
colnames(FDH_Summary) <- c("Method","Eff", "P1", "P2", "P3", "L1", "L2", "L3", "L4", "L5", "L6")
print(FDH_Summary)
```



```{r}
# DEA code utilizing the CRS method
CRS <- rep("CRS", times = 6)
DEA_CRS <- dea(X, Y, RTS = "CRS")
DEA_CRS_Peers <- peers(DEA_CRS)                             
DEA_CRS_Lambda <- lambda(DEA_CRS)                            
print(DEA_CRS)
print(DEA_CRS_Peers)
print(DEA_CRS_Lambda)
dea.plot.isoquant(X, Y, RTS= "CRS")
DEA_CRS_Lambda <- cbind(DEA_CRS_Lambda, Not_Applicable, Not_Applicable)
CRS_Summary <- cbind(CRS, DEA_CRS$eff, DEA_CRS_Peers, DEA_CRS_Lambda)
colnames(CRS_Summary) <- c("Method","Eff", "P1", "P2", "P3", "L1", "L2", "L3", "L4", "L5", "L6")
CRS_Summary <- as.data.frame(CRS_Summary)
CRS_Summary
```


```{r}
# DEA code utilizing the VRS method
VRS <- rep("VRS", times = 6)
DEA_VRS <- dea(X, Y, RTS = "VRS")
DEA_VRS_Peers <- peers(DEA_VRS)                             
DEA_VRS_Lambda <- lambda(DEA_VRS)                            
print(DEA_VRS)
print(DEA_VRS_Peers)
print(DEA_VRS_Lambda)
dea.plot.isoquant(X, Y, RTS= "VRS")
DEA_VRS_Lambda <- cbind(DEA_VRS_Lambda, Not_Applicable)
VRS_Summary <- cbind(VRS, DEA_VRS$eff, DEA_VRS_Peers, DEA_VRS_Lambda)
colnames(VRS_Summary) <- c("Method","Eff", "P1", "P2", "P3", "L1", "L2", "L3", "L4", "L5", "L6")
VRS_Summary <- as.data.frame(VRS_Summary)
VRS_Summary
```


```{r}
# DEA code utilizing the IRS method
IRS <- rep("IRS", times = 6)
DEA_IRS <- dea(X, Y, RTS = "IRS")
DEA_IRS_Peers <- peers(DEA_IRS)                             
DEA_IRS_Lambda <- lambda(DEA_IRS)                            
print(DEA_IRS)
print(DEA_IRS_Peers)
print(DEA_IRS_Lambda)
dea.plot.isoquant(X, Y, RTS= "IRS")
DEA_IRS_Lambda <- cbind(DEA_IRS_Lambda, Not_Applicable)
IRS_Summary <- cbind(IRS, DEA_IRS$eff, DEA_IRS_Peers, DEA_IRS_Lambda)
colnames(IRS_Summary) <- c("Method","Eff", "P1", "P2", "P3", "L1", "L2", "L3", "L4", "L5", "L6")
IRS_Summary <- as.data.frame(IRS_Summary)
IRS_Summary
```

```{r}
# DEA code utilizing the DRS method
DRS <- rep("DRS", times = 6)
DEA_DRS <- dea(X, Y, RTS = "DRS")
DEA_DRS_Peers <- peers(DEA_DRS)                             
DEA_DRS_Lambda <- lambda(DEA_DRS)                            
print(DEA_DRS)
print(DEA_DRS_Peers)
print(DEA_DRS_Lambda)
dea.plot.isoquant(X, Y, RTS= "DRS")
DEA_DRS_Lambda <- cbind(DEA_DRS_Lambda, Not_Applicable, Not_Applicable)
DRS_Summary <- cbind(DRS, DEA_DRS$eff, DEA_DRS_Peers, DEA_DRS_Lambda)
colnames(DRS_Summary) <- c("Method","Eff", "P1", "P2", "P3", "L1", "L2", "L3", "L4", "L5", "L6")
DRS_Summary <- as.data.frame(DRS_Summary)
DRS_Summary
```


```{r}
# DEA code utilizing the ADD method
ADD <- rep("ADD", times = 6)
DEA_ADD <- dea(X, Y, RTS = "ADD")
DEA_ADD_Peers <- peers(DEA_ADD)                             
DEA_ADD_Lambda <- lambda(DEA_ADD)                            
print(DEA_ADD)
print(DEA_ADD_Peers)
print(DEA_ADD_Lambda)
DEA_ADD_Peers <- cbind(DEA_ADD_Peers, Not_Applicable, Not_Applicable)
ADD_Summary <- cbind(ADD, DEA_ADD$eff, DEA_ADD_Peers, DEA_ADD_Lambda)
colnames(ADD_Summary) <- c("Method","Eff", "P1", "P2", "P3", "L1", "L2", "L3", "L4", "L5", "L6")
ADD_Summary <- as.data.frame(ADD_Summary)
ADD_Summary
```

```{r}
# Combine all of the method summary tables into one large summary table for each method
Summary_Table <- rbind(FDH_Summary, CRS_Summary, VRS_Summary, IRS_Summary, DRS_Summary, ADD_Summary)
print(Summary_Table)
```

The summary table reveals that the FRH and FDH techniques both return efficiency of 1.0 for all six DMUs, as well as the same peer and lambda values. DMU[1:4] was discovered by the CRS approach to be effective at 1.0. DMU[1:5] was discovered by the VRS approach to be effective at 1.0. DRS and IRS both found DMU[1:5] to be efficient at 1.0, as did the DMU[1:4] technique. The Peer[1] and Peer[2] values for all of the less effective DMUs were 1 and 2, respectively, although the Peer[3] value varied between 4 and 5. Additionally, for the identical DMU across all approaches, the relative weights (lambdas) were rather close.
